A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum sequential games with imcomplete information

### 2015-07-10 paper.tex
refactors + fixups + some XXX removal

\documentclass[a4paper,9pt,journal]{IEEEtran}
\usepackage{graphicx} \usepackage[cmex10]{amsmath}
\usepackage{amssymb} \usepackage{fancybox} \usepackage{alltt}
\usepackage{soul} \usepackage{color} \usepackage{verbatim}
\usepackage{xcolor} \usepackage{colortbl,hhline}
\usepackage[ruled,vlined]{algorithm2e} \usepackage{framed}
\usepackage{amsthm} \usepackage{fancyref}
\usepackage{amsmath,amsfonts,amssymb, amsthm} \usepackage{textcomp}

\newtheorem{remark}{Remark}

\def \lb {{\langle}} \def \rb {{\rangle}}
\newcommand{\fro}[1]{\|#1\|_2}
\newcommand{\theHalgorithm}{\arabic{algorithm}}

\newcommand{\argmin}{\mathop{\mathrm{argmin}}}

\usepackage{hyperref}

\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}

\newcommand{\prox}{\textrm{pr ox} } \newcommand{\grad}{\textrm{grad} }
\newcommand{\dive}{\textrm{div} }

\pagenumbering{gobble}

\begin{document}
%\onecolumn
\title{A fast primal-dual algorithm for computing Nash equilibria and best response strategies in two-person zero-sum sequential games}

\author{\IEEEauthorblockN{Elvis D. DOHMATOB}}

\maketitle

\begin{abstract}
% LESS THAN 200 WORDS !!!!!
% 
% While medical imaging typically provides massive amounts of
% data, the extraction of relevant information in a given
% applicative context remains a difficult challenge.
% XXX : don't call it SPM but just "predictive regions or predictive
% maps"
In this manuscript, we consider the problem of computing a best response against an opponent's realization plan in two-person sequential games.
The proposed algorithm for solving the corresponding contrained convex-optimization problem, derives from the primal-dual scheme of A. Chambolle and T. Pock.
Our algorithm is simple: all resolvent operators can be effectively computed in closed-form, using only elementary algebraic operations.
%%  and is orders of magnitude more efficient than state-of-the-art algorithms like those based on Linear Programming, Interior-Point methods,
%% and more recently, the Nesterov Excessive Gap Technique.
% By way of example, we conclude by exhibiting results on Texas Hold'em Poker.
\end{abstract}

\begin{IEEEkeywords}
  game theory; two-person sequential game; Nash equilibria; best response; convex-optimization; contraint; primal-dual scheme
\end{IEEEkeywords}

\section{Introduction}
%\label{sec:intro}
\subsection{Notation and Terminology}
To begin, let us introduce some technical notation and terminology we will be using in this paper. The reader should lookup any standard textbook
(for example \cite{boyd2004}) on convex optimization for a tutorial introduction to these notions. Viz,
\begin{itemize}
\item $\mathbb{R}^{m \times n}$: \quad space of all $m$-by-$p$ real matrices;
\item $E^{-1}(U)$: \quad pre-image of $U \subset \mathbb{R}^n$ under a matrix $E \in \mathbb{R}^{p,n}$,
namely the set $\{x \in \mathbb{R}^n\text{ }| \text{ }Ex \in U\}$
\item $A^T$: \quad transpose of a matrix $A$;
\item $\begin{bmatrix}A\\B\end{bmatrix}$: \quad vertical stacking of two matrices $A$ and $B$;
\item $v_j$: \quad $j$th component of  a vector $v$;
\item $u^Tv$: \quad dot product of two vectors $u$ and $v$;
\item $\mathbb{R}^n_+$: \quad the $n$-dimensional nonnegative orthant;
\item $(x)_+$: \quad component-wise maximum of a vector $x$ and 0;
\item $i_C$: \quad indicator function of a convex set $C$;
\item $\Pi_C$: \quad euclidean projector onto a convex set $C$;
\item $\|K\|_2$: \quad matrix 2-norm of a matrix $K$;
\item \textit{l.s.c.p.c}: \quad acronym for adjective \textit{lower semi-continuous proper convex};
\item $f^*$: \quad Fenchel transform (a.k.a convex conjugate) of a \textit{l.s.c.p.c} function $f$;
\item $(1 + \sigma \partial f)^{-1}$: resolvent (a.k.a proximal) operator of a \textit{l.s.c.p.c} function $f$, for a given stepsize $\sigma > 0$
\end{itemize}

\subsection{Statement of the problem}
Consider a two-person sequential game\footnote{In a sequential game, players take turns in play, one after the other,
as opposed to simultaneous play.} in \textit{sequential-form} (See for example, \cite{von1996efficient}
and \cite{koller1996efficient} 
for theory on sequential-form representation), and let $A \in \mathbb{R}^{m,n}$ be our payoff matrix.
We will be referring to the other player as ``the opponent''. We are interested in the problem of
finding a best response strategy $x^* \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})$, given a fixed
behavioral strategy $y_0$ for the opponent, where $E$ is a sparse $p$-by-$n$ matrix whose
entries are $-1$, $0$, or $+1$, and $(1, 0, 0, ..., 0) =: e \in \mathbb{R}^p$. Recall that $E$
and $e$ encode linear constraints on our ``admissible'' realization plans\footnote{In games
in sequential form, the terms ``strategy'' and ``realization plan'' mean thesame thing.} $x$,
in the sequential form representation of the game. In the language of convex-optimization,
one can readily give the following saddle-point formulation for this problem. Viz,

\begin{equation}
  \underset{x \in \mathbb{R}_{+}^n \cap E^{-1}(\{e\})}{min}\text{ }-y_0^TAx
  \label{eq:opt_pb}
\end{equation}

\begin{definition}
A solution $x^*$ to problem \eqref{eq:opt_pb} is called a \textit{best response} strategy against
the opponent's fixed strategy $y_0$.
\end{definition}

\begin{remark}
Of course $y_0$ is not necessarily an optimal strategy for the opponent. In case it is, the pair $(x^*, y_0)$
is a Nash equilibrium for the game.
\end{remark}

\begin{remark}
  In practice, $A$, $E$, and $F$ are very sparse.
%% : $A$ will be sparse because a concrete sequential game will
%% typically have very few\footnote{Few, relative to the size of the game tree.} leafs, and only a few
%% combinations of sequences of moves of the players, will actually lead to a leaf (i.e. end the game);
%% $E$ and $F$ will be sparse because the kinks of possible sequences of moves of each player will
%% zig-zag between only a limited number of the player's information sets so that a move at an information set will
%% rarely\footnote{Relative to the number of information sets for the player.}  extend another information set.
This sparsity should be thoroughly exploited\footnote{For example when
multiplying vectors with these matrices.} by a solver for problem \eqref{eq:opt_pb}.
\end{remark}

In section \ref{sec:related_work}, we give a brief overview of existing methods for solving \eqref{eq:opt_pb}.
We elaborate our proposed algorithm in section \ref{sec:algo}.

\section{Related work}
\label{sec:related_work}

Pending...

\section{The proposed algorithm}
\label{sec:algo}
In this section we present the algorithm which is the purpose of this paper, namely an algorithm
for solving \eqref{eq:opt_pb}. Our algorithm (Alg.\ref{Tab:algo}) is a use-case of
the generic primal-dual algorithm of A. Chambolle and T. Pock, namely Algorithm 1 of \cite{chambolle2010}.

\subsection{Derivation of the algorithm}
First observe that (1) can be re-written in the form:
\begin{equation}
  \underset{x \in \mathbb{R}^n}{min}\text{ }{f(-Ax) + g(x)}
\end{equation}
where:\\
\begin{equation}
  \left.
  \begin{aligned}
    g := i_{E^{-1}(\{e\})} + i_{\mathbb{R}_{+}^m}\\
    f: z \mapsto y_0^Tz
    \end{aligned}
  \right\}
\end{equation}

Finally, the primal-dual formulation of this problem (which can be easily obtained using
\textit{Fenchel-Rockafellar duality}, for example) is:
\begin{equation}
  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m}{max}\text{ }{y^T(-A)x_0 + g(x) - f^*(y)}
\end{equation}

Now, let's observe that $i_{E^{-1}(\{e\})}(x) = \underset{\zeta \in \mathbb{R}^p}{max}\text{ }\zeta^T(e - Ex)$, and so one can re-write (2) as:
\begin{equation}
  \underset{x \in \mathbb{R}^n}{min}\text{ }\underset{y \in \mathbb{R}^m, \zeta \in \mathbb{R}^p}{max}\text{ }
  \begin{bmatrix}y\\\zeta\end{bmatrix}^TKx + G(x) - F^*(y, \zeta)
  \label{eq:pd_opt}
\end{equation}
where we've defined:
\begin{equation}
  \left.
  \begin{aligned}
    K := -\begin{bmatrix}A\\E\end{bmatrix}\\
    G := g - i_{E^{-1}(\{b\})} = i_{\mathbb{R}_{+}^n}\\
    F^*: (y, \zeta) \mapsto (f^*(y) - \zeta^Te) = (i_{\{y_0\}}(y) - e^T\zeta)
  \end{aligned}
  \right\}
\end{equation}

Furthermore, one easily checks that $F^*$ and $G$ are \textit{l.s.c.p.c} with resolvent
(a.k.a \textit{proximity}) operators given by the simple formulae:
\begin{equation}
  \left.
  \begin{aligned}
    (1 + \tau \partial G)^{-1} = \Pi_{\mathbb{R}_+^n}: x \mapsto (x)_+\\
    (1 + \sigma \partial F^*)^{-1}: (y, \zeta) \mapsto (y_0, \zeta + \sigma e)
  \end{aligned}
  \right\}
\end{equation}

Using these ingredients, we derive the primal-dual algorithm given in Alg.\ref{Tab:algo}, 
for solving \eqref{eq:pd_opt}, and thus \eqref{eq:opt_pb}.

\begin{remark}
Equation \eqref{eq:pd_opt} is in the form of equation (2) in \cite{chambolle2010} if we take $X := \mathbb{R}^n$ and
$Y := \mathbb{R}^m \times \mathbb{R}^p$.
\end{remark}

\begin{remark}
Neither $G$ nor $F^*$ is strongly convex and so Alg.\ref{Tab:algo} cannot be accelerated in the sense of algorithm 39 of \cite{chambolle2010}.
\end{remark}

\begin{algorithm}[htb]
  \caption{Primal-dual algorithm for computing best response against opponent's fixed realization plan $y_0$}
  \textbf{Given} Tolerance $\epsilon > 0$.\\
  \textbf{Initialize} $\tilde{x^{(0)}} = x^{(0)} \in \mathbb{R}^n$; $\zeta^{(0)} \in \mathbb{R}^{q}$;
  $\tau, \sigma > 0 \text{ s.t. }\tau\sigma \|K\|_2^2 < 1$; $k = 0$.\\
  \textbf{Precompute} $\eta_0 \leftarrow \tau A^Ty_0$\\
  \Repeat{
    $\frac{\|x^{(k+1)} - x^{(k)}\|^2_2}{2\tau} + \frac{\|\zeta^{(k+1)} - \zeta^{(k)}\|^2_2}{2\sigma} < \epsilon$}{
    \begin{eqnarray*}
      \zeta^{(k+1)} &\leftarrow& \zeta^{(k)} - \sigma \bigl(e - E\tilde{x}^{(k)}\bigr)\\
      x^{(k+1)} &\leftarrow& \bigl(x^{(k)} + \eta_0 + E^T\zeta^{(k+1)}\bigr)_+\\
      \tilde{x}^{(k+1)} &\leftarrow& 2x^{(k+1)} - x^{(k)}\\
      k &\leftarrow& k + 1
    \end{eqnarray*}
  } \Return $x^{(k)}$, $-y_0^TAx^{(k)}$
  \label{Tab:algo}
\end{algorithm}

\subsection{Convergence analysis of the algorithm}
Pending...

\begin{remark}
The derivation above reveals that in equation \eqref{eq:opt_pb} above, if the constraint ``$x \ge 0$'' is replaced by
a constraint ``$x \in C$'' (thus obtaining a new problem) where $C$ is a convex set
%% onto which euclidean projections
%% can be easily computed (for example, a probability simplex)
, then we simply need to replace the operator ``$(.)_+$''
with ``$\Pi_C$'' in the equations to obtain a corresponding algorithm. Of course, this is because $i_C^* = \Pi_C$.
\end{remark}

\medskip \noindent
\textbf{Acknowledgments:}
Pending...

% ==========
% = biblio =
% ==========
% {\small
\bibliographystyle{IEEEtran} \bibliography{IEEEabrv,bib_tv.bib,agt.bib}
\end{document}

%
%

>>>>

\documentclass{article} % For LaTeX2e
\usepackage{nips14submit_e}
%\documentclass[envcountsame]{llcns2e/llncs}
\usepackage{url}
\usepackage{times}
\usepackage{amsmath,amsfonts, amsthm}
\usepackage{bbm}
\usepackage{algorithm,algorithmicx}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{bbm}
\usepackage[titletoc]{appendix}
\usepackage{algpseudocode}
\usepackage{pifont}
\usepackage[FIGTOPCAP]{subfigure}

\newtheorem{theorem}{Theorem} \newtheorem{lemma}[theorem]{Lemma}

\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}{Remark}
\newtheorem{fact}{Fact}

\DeclareMathOperator{\proj}{proj}
\DeclareMathOperator{\prox}{prox}

\title{
  %\hrule\hrule\bigskip\bigskip
  A simple and efficient algorithm for computing approximate
  Nash equilibria in two-person zero-sum sequential games with imcomplete
  information}
\author{Elvis DOHMATOB
\\Parietal team, Inria Saclay Ile-de-France, Saclay, France
\\\texttt{firstname.lastname@inria.fr}
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

%\nipsfinalcopy % Uncomment for camera-ready version
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle
\begin{abstract}We present a simple primal-dual algorithm for
  computing approximate Nash equilibria in two-person zero-sum
  sequential games with  imcomplete information and perfect recall
  (like Texas Hold'em Poker) based on the notion of enlarged
  subgradients. Our algorithm only performs basic iterations (i.e
  iterations involving no calls to external first-order oracles, etc.)
  and is applicable to a broad class of two-person zero-sum games
  including simultaneous games and sequential games with imcomplete
  information and perfect recall. The applicability to the latter kind
  of games is thanks to the sequence-form representation
  \cite{koller1992complexity} which allows us to encode any such game
  as a matrix game with polyhedral strategy profiles, the size of the
  representation being linear in ... The number of iterations needed
  to produce a Nash equilibrium with a given precision is inversely
  proportional to the desired precision. As proof-of-concept, we apply our
  algorithm to solve Kuhn 3-card Poker.
\end{abstract}

\textbf{keywords}: sequential game; imcomplete information; perfect
recall; sequence-form; approximate Nash equilibrium; primal-dual
algoithm; convex-optimization; enlarged subgradient

\section{Introduction}
\label{sec:intro}
A game-theoretic approach to playing games strategically optimally
consists in computing Nash-equilibria (infact, approximations thereof)
offline, and playing one's part of the equilibrium online. This
technique is the driving-force behind solution concepts like CFR
\cite{zinkevich2008regret,lanctot2009monte},
$\text{CFR}^{+}$ \textbf{TODO: add ref!!!}, and other variants, which
have recently had profound success in Poker. However, solving games
for equilibria remains a mathematical and computational challenge,
especially in sequential games with imperfect information. This paper
proposes a simple and fast algorithm for solving for such equilibria
approximately, in a sense which will be made clear shortly.

\subsection{Notation and terminology}
\paragraph{\textbf{General notions.}}
Given a set $X$, $2^X$ denotes the \emph{powerset} of $X$, i.e the set
of all subsets of $X$, or equivalently the set of all binary
functions on $X$.

Let $m$ and $n$ be positive integers.
$\mathbb{R}^{n}_+ := \{z \in \mathbb{R}^{n}\text{ }|\text{ } z \geq
0\}$ is the nonnegative $n$-dimensional \textit{orthant}.  Given two
vectors $z, w \in \mathbb{R}^n$, their inner product will be denoted
$\langle z, w\rangle := \sum_{j}z_jw_j$ The components of $z \in \mathbb{R}^n$ will be
denoted $z_0$, $z_1$, ..., $z_{n-1}$ (indexing begins from $0$,
not $1$). The notation ``$z \ge 0$'' means that all the components of $z$ are
nonnegative. For a vector $z = (z_0, z_1, ..., z_{n-1}) \in
\mathbb{R}^n$, $\|z\|$ denotes the $2$-\textit{norm} of $z$ defined
by $\|z\| := \sqrt{\langle z, z\rangle}$.
$(z)_+:=\text{max}(0, z) \in \mathbb{R}^{n}_+$ is the point-wise
maximum of $z$ with $0$. For example, $((-2, \pi))_+ = (max(-2, 0),
max(\pi, 0)) = (0, \pi)$.
The operator $(.)_+$ is the well-known
(multi-dimensional) \textit{ramp} function.

Given a matrix $A \in \mathbb{R}^{m \times n}$, its \textit{spectral
  norm}, denoted $\|A\|$, is
 defined to be the largest \textit{singular value} of $A$, i.e the
 largest \textit{eigenvalue} of $A^TA$ (or equivalently, of $AA^T$).

\paragraph{\textbf{Convex analysis.}}
Given a subset $C$ of $\mathbb{R}^n$,
$i_C$ denotes its \textit{indicator function} defined by
\begin{eqnarray}
  i_C(x) = 0 \text{ if } x \in C\text{ and }+\infty\text{
    otherwise.}
\end{eqnarray}
At times, we will write $i_{x \in C}$ for $i_C(x)$ (to ease notation,
etc.). Let $f : \mathbb{R}^n \rightarrow (-\infty, +\infty]$ be a
  convex function. The \textit{effective domain} of $f$, denoted
  $dom(f)$, is defined as
\begin{eqnarray}
  dom(f) := \{x \in \mathbb{R}^n | f(x) < +\infty\}.
\end{eqnarray}
 If $dom(f) \ne \emptyset$ then we say $f$ is \textit{proper}.
%% \textit{proper convex lower semi-continous function}
%% (\textit{p.c.l.s.c} for short).
%% The \textit{Fenchel-Legendre transform} of $f$ is the function $f^*:
%% \mathbb{R}^n \rightarrow (-\infty, +\infty]$ defined by $f^*(x) \equiv
%%   \underset{z \in \mathbb{R}^n}{\text{max}}\text{}z^Tx - f(z)$.
The \textit{subgradient} of $f$ is the set-valued function
\begin{eqnarray}
\partial f: \mathbb{R}^n \rightarrow 2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto
\{s\in \mathbb{R}^n | f(z)  \ge f(x) + \langle s, z - x\rangle, \forall
z \in \mathbb{R}^n\}.
\end{eqnarray}
Of course $\partial f(x)$ reduces to the singleton $\{\nabla f(x)\}$
in case $f$ is differentiable at $x$. If $f$ is convex, its
\textit{proximal operator} is the function $\prox_f: \mathbb{R}^n
\rightarrow \mathbb{R}^n$ defined by
\begin{eqnarray}
  \prox_f(x): = \underset{z \in \mathbb{R}^n}{\text{min }}\frac{1}{2}\|z
  - x\|^2 + f(z).
\end{eqnarray}
For example, if $C$ is a closed convex subset of $\mathbb{R}^n$, then
$\prox_C = \proj_C$, the orthogonal projector onto $C$. Thus proximal
operators generalize orthogonal projectors. One also has the useful
characterization
\begin{eqnarray}
  p = \prox_f(x)\text{ iff } x - p \in \partial f(p).
\end{eqnarray}

The interested reader should refer to \cite{combettes2011proximal} for
a more elaborate exposition of proximal operators and their
use in modern convex-optimization.

\subsection{Statement of the problem}
The sequence-form for two-person zero-sum games was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium}, where it was
established that for sequential two-person zero-sum games with
imcomplete information and perfect recall, there exist sparse matrices
$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
$l_1$, and $l_2$ are all linear in the size of the game tree (number
of states in the game) and such that Nash equilibria correspond to
pairs $(x, y)$ of \textit{realization plans} which solve the primal
LCP
\begin{equation}
  \begin{aligned}
     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

and the dual LCP
\begin{equation}
  \begin{aligned}
    \text{maximize}-\langle e_2, q\rangle,\hspace{.5em}\text{subject
      to: }(x,q) \in \mathbb{R}^{n_1} \times \mathbb{R}^{l_2},  x \ge
    0, E_1x = e_1, A^Tx + E_2^Tq \geq 0.
  \end{aligned}
  \label{eq:dual_pb}
\end{equation}
The vectors $p = (p_0, p_1, ..., p_{l_2 - 1}) \in \mathbb{R}^{l_2}$
and $q = (q_0, q_1, ..., q_{l_1 - 1}) \in \mathbb{R}^{l_1}$ are dual
variables. 
$A$ is the \textit{payoff matrix} and each $E_k$ is a matrix whose
entries are $-1$, $0$ or $1$, and each $e_k$ is a vector of the form
$(1, 0, ..., 0)$. In this so-called \textit{sequence-form}
representation, the strategy profile of player $k$ is the polyhedron
\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}_+ |\text{ }E_kz = e_k\}.
\label{eq:polyhedron}
\end{equation}

Note that the LCPs above have the equivalent saddle point formulation
\begin{equation}
  \underset{y \in Q_2}{\text{minimize}}\text{ }\underset{x \in
    Q_1}{\text{maximize}}\text{ }\langle x, Ay\rangle
  \label{eq:gilpin}
\end{equation}

%% Note that $\langle e_1, p\rangle = p_0$ and $\langle e_2, q\rangle
%% = q_0$ by definition of $e_1$ and
%% $e_2$. 
At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
$\mathcal{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{equation}
  0 \le \mathcal{G}(y, p, x, q) := \langle e_1, p\rangle - (\langle
  e_2, q\rangle) = \langle e_1, p\rangle + \langle
  e_2, q\rangle = G(x, y),
  \label{eq:dgap}
\end{equation}
where
\begin{eqnarray}
G(x, y) :=
\mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
(u,v) \in Q_1 \times Q_2\}.
\label{eq:xy_gap}
\end{eqnarray}

%\subsection{Characterization of equilibria}
It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
$(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a Nash
equilibrium for the game)  if and only if there exist vectors $p$ and
$q$ such that
\begin{equation}
\hspace{.25em} -Ay + E_1^Tp \ge 0, \hspace{.5em}A^Tx + E_2^Tq \ge
0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0, \hspace{.25em}
\langle y, A^Tx  + E_2^Tq\rangle = 0.
\label{eq:feasibility}
\end{equation}

Moreover, at equilibria, \textit{strong duality} holds and the value
of the game equals $p_0 = -q_0$, i.e the primal-dual gap
$\mathcal{G}(y, p, x, q)$ defined in \eqref{eq:dgap} vanishes at
equilibria.

%% As usual, the ``minimax'' notation in problem \eqref{eq:primal_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution if (and only if)
%% \begin{equation}
%%   x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
%% \label{eq:nash_ineq}
%% \end{equation}
%% Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
%% \footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.

\begin{remark}  
It should be noted that for the class of games considered here
(sequential games with imcomplete information), the LCPs
\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
than what state-of-the-art LCP solvers can handle. See
\cite{hoda2010smoothing}.

\end{remark}

Solving the LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} exactly
is impossible in practice \textbf{Cite Koller!!!}, and such a
precision doesn't have any fundamental advantage. Instead, it is
customary compute so-called Nash $\epsilon$-equlibria.

\begin{definition}[\textbf{Nash $\epsilon$-equilibria}]
Given $\epsilon > 0$, a Nash $\epsilon$-equilibrium is
a pair $(x^*, y^*)$ of realization plans such that there exists dual
vectors $p^*$ and $q^*$ for problems \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} such that the primal-dual gap at $(y^*, p^*, x^*, q^*)$
doesn't exceed $\epsilon$. That is,

\begin{equation}
  0 \le \mathcal{G}(y^*, p^*, x^*, q^*) \le \epsilon.
\label{eq:approx_pb}
\end{equation}
\label{thm:approx_nash}
\end{definition}

Let us introduce the notion of $\epsilon$-subgradients
\cite{he2013accelerating}.

\begin{definition}[$\epsilon$-subgradient]
Given a scalar $\epsilon > 0$ and a function $f:\mathbb{R}^n
\rightarrow [-\infty,+\infty]$, the $\epsilon$-enlarged subgradient (or
$\epsilon$-subgradient, for short) of $f$ is the set-valued function
\begin{eqnarray}
\partial_\epsilon f: \mathbb{R}^n \rightarrow
2^{\mathbb{R}^n}, \hspace{.5em} x \mapsto \{s \in \mathbb{R}^n | f(z)
\ge f(x) + \langle s, z - x\rangle - \epsilon,\forall z \in
\mathbb{R}^n\}.
\end{eqnarray}
\end{definition}

The idea behind $\epsilon$-subgradients is the following. Say we wish
to minimize the function $f$. Replace the usual necessary
condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
weaker condition ``$\partial_\epsilon f(x)$ contains a sufficiently
small vector $v$''. In fact, it is easy to see that, for each
point $x \in \mathbb{R}^n$, we have $\underset{\epsilon \rightarrow
  0^+}{\text{lim }}\partial_\epsilon f(x) = \partial f(x)$.
This approximation concept for subgradients yields the following
concept of approximate Nash equlibria (adapted from
\cite{he2013accelerating}).

\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
Given $\rho > 0$ and $\epsilon > 0$, a Nash
$(\rho,\epsilon$)-equilibrium for the GSP \eqref{eq:unconstrained_pb}
is any quadruplet $(x^*, y^*, x^*, q^*)$ for which
there exists a perturbation vector $v^*$ such that
\begin{eqnarray}
\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
  \hat{\Psi}_2(y^*, p^*, , .)](y^*,p^*,x^*,q^*).
\end{eqnarray}

Such a vector $v^*$ is called a Nash $\epsilon$-residual at $(x^*,
y^*, x^*, q^*)$.
\label{thm:cool_notion}
\end{definition}

The above definition is a generalization of the notion of Nash
equilibria since:
\begin{itemize}
\item Exact Nash equilibria correspond to Nash $(0^+,0^+)$-equilibria.
\item Nash $\epsilon$-equilibria (in the sense of Definition
  \ref{thm:approx_nash}) correspond to Nash $(0^+,\epsilon)$-equilibria.
\end{itemize}

\subsection{Our contribution}
We develop a $\mathcal{O}(1/\text{min}(\rho,\epsilon))$ primal-dual
algorithm (Algorithm \ref{Tab:algo}) for computing Nash $(\rho,
  \epsilon$)-equilibria for sequential two-person zero-sum games with
  imcomplete information and perfect recall.

\section{Related work}
\label{sec:related_work}
\textbf{TODO: add note about interior-point methods!!!}

We present a selection of algorithms that is representative of the
efforts that have been made in the literature to compute Nash
$\epsilon$-equilibria for two-person zero-sum games with imcomplete
information like Texas Hold'em Poker, etc.

In \cite{hoda2010smoothing}, a nested iterative procedure using the
Excessive Gap Technique (EGT) \cite{nesterov2005excessive} was used to
to solve the equilibrium problem \eqref{eq:gilpin}.
The authors reported a $\mathcal{O}(1/\epsilon)$ convergence rate
(which derives from the general EGT theory) for the outer-most
iteration loop.

\cite{gilpinfirst} proposed a modified verson of the technqiues in
\cite{hoda2010smoothing} and  proved a $\mathcal{O}\left(\left(\|A\| /
\delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate in
terms of the number of calls made to a first-order oracle. Here
$\delta = \delta(A, E_1, E_2, e_1, e_2) > 0$ is a certain
\textit{condition number} for the game. The crux of their technique was to
observe that \eqref{eq:gilpin} can further be written a the minimization of
the primal-dual gap function $G(x, y)$ (defined in \eqref{eq:xy_gap})
for the game\footnote{The minimizers of $G$ are precisely the
  equilibria of the game.}, viz
\begin{eqnarray}
\mathrm{maximize}\{G(x,y)|(x,y) \in Q_1 \times Q_2\},
\end{eqnarray}
and then show there exists a scalar
$\delta > 0$ such that for any pair of realization plans $(x, y) \in Q_1 \times Q_2$,
\begin{eqnarray}
\text{``distance between }(x, y)\text{ and the set of
equilibria'' } \le G(x, y)/\delta.
\end{eqnarray}
Their
algorithm is then derived by iteratively applying Nesterov smoothing \cite{nesterov2005a}
with a geometrically decreasing sequence of tolerance levels
$\epsilon_{n+1} = \epsilon_n / \gamma$ (with $\gamma > 1$)  $G$. It
should be noted however that
\begin{itemize}
\item[--] The constant $\delta > 0$ can be arbitrarily small, and so
  the factor $\|A\| / \delta$ in the $\mathcal{O}\left(\left(\|A\| /
\delta\right) ln\left(1 / \epsilon\right)\right)$ convergence rate can
be arbitrarily large.
\item[--] The reported linear convergence rate is not in terms of
  basic operations (addition, multiplication, matvec, clipping, etc.),
  but in terms of the number of calls to a first-order oracle. For
  example the projections $\proj_{Q_k}$ are applied at each iteration.%%  Of
  %% course, the existence of a linear algorithm for solving
  %% \eqref{eq:gilpin} is improbable, as the usual strong-convexity
  %% conditions are absent.

\end{itemize}

%% It should be noted that the EGT and its precursors have had
%% considerable success in the signal processing communities, as can
%% be seen in \cite{NestaCandès, eduard, etc.} and the references
%% therein.

The primal-dual algorithm first developed in \cite{chambolle2010} was
proposed \cite{chambolle2014ergodic} in to solve matrix games on
simplexes. It should be stressed that such matrix games are
considerably simpler than the games considered here. Indeed, the
authors in \cite{chambolle2014ergodic} use the fact that computing the
euclidean projection of a point unto a simplex can be done in linear
time as in \cite{duchi2008efficient}. In contrast, no such efficient
algorithm is known nor is likely to exist for the polyhedra $Q_k$
defined in \eqref{eq:polyhedron}, the strategy profiles for players in
the games considered here. It should however be noted that such this
projection can still be done iteratively using, for example, the
algorithm in proposition 4.2 of \cite{combettes2010dualization}%%  or any
%% CQ algorithm (since this projection sub-problem, is, in fact a
%% \textit{split-feasibility problem}), for example
. Unfortunately, as
with any nested iterative scheme, one would have to solve this
sub-problem with finer and finer precision.

Sampling techniques like the CFR (CounterFactual Regret minimization)
and its many variants
\cite{MartinZinkevichNIPS2007,lanctot2009monte,Bowling09012015} have
also become state-of-the-art.

\section{Reformulation as a Generalized Saddle-point Problem (GSP)}
\label{sec:gsp}
One cannot directly attack the LCPs \eqref{eq:primal_pb} and
\eqref{eq:dual_pb} via a traditional primal-dual algorithm
(for example \cite{chambolle2010,chambolle2014ergodic}) because
computing the euclidean projections $\proj_{Q_k}$ is very difficult
(in fact, such subproblems would have to be solved
iteratively\footnote{An ``exception to the rule'' is the case where
  the $Q_k's$ are simplexes, so that the projections can be computed
  exactly using \cite{duchi2008efficient}.}). Also,
the primal-dual gap might explode even at ``nearly feasible'' points,
leaving a primal-dual algorithm with no clear on whether progress is
being made or not. So need to way to
\begin{itemize}
\item[--] avoid having to compute the projections $\proj_{Q_k}$,
\item[--] have control over how far we are from the set of equilibria and
  avoid infinite (and thus non-informative) primal-dual gaps.
\end{itemize}

In the next theorem, we show that the said LCP problems can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{y \ge 0} + \langle e_1,p\rangle\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{x \ge 0} + \langle e_2, q\rangle
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}
